\bibitem[LDAP]{LDAP}Lightweight Directory Access Protocol (LDAP): Technical
Specification Road Map, K. Zeilenga, Ed.[06.2006]
%\bibitem[SBQL]{SBQL}Stack-Based Approach (SBA) and Stack-Based Query Language
%(SBQL). Kazimierz Subieta, [03.12.2006], (http://www.sbql.pl)
\bibitem[RFC4511]{RFC4511} Sermersheim, J., Ed., "Lightweight Directory Access
                 Protocol (LDAP): The Protocol", RFC 4511, June 2006.
\bibitem[RFC4512]{RFC4512} Zeilenga, K., "Lightweight Directory
   Access Protocol (LDAP): Directory Information Models", RFC 4512, June
                 2006.
\bibitem[RFC4513]{RFC4513} Harrison, R., Ed., "Lightweight Directory
   Access Protocol (LDAP): Authentication Methods and Security
                 Mechanisms", RFC 4513, June 2006.
\bibitem[RFC4514]{RFC4514} Zeilenga, K., Ed., "Lightweight Directory
   Access Protocol (LDAP): String Representation of Distinguished
                 Names", RFC 4514, June 2006.
\bibitem[RFC4515]{RFC4515} Smith, M., Ed. and T. Howes, "Lightweight
   Directory Access Protocol (LDAP): String Representation of Search
                 Filters", RFC 4515, June 2006.
\bibitem[RFC4516]{RFC4516} Smith, M., Ed. and T. Howes, "Lightweight
   Directory Access Protocol (LDAP): Uniform Resource Locator", RFC
                 4516, June 2006.
\bibitem[RFC4517]{RFC4517}  Legg, S., Ed., "Lightweight Directory
   Access Protocol (LDAP): Syntaxes and Matching Rules", RFC 4517, June
                 2006.
\bibitem[RFC4519]{RFC4518} Zeilenga, K., "Lightweight Directory
   Access Protocol (LDAP): Internationalized String Preparation", RFC
                 4518, June 2006.
\bibitem[RFC4519]{RFC4519} Sciberras, A., Ed., "Lightweight
   Directory Access Protocol (LDAP): Schema for User Applications", RFC
                 4519, June 2006.
\bibitem[RFC5420]{RFC4520} Zeilenga, K., "Internet Assigned Numbers
   Authority (IANA) Considerations for the Lightweight Directory
                 Access Protocol (LDAP)", BCP 64, RFC 4520, June 2006.
\bibitem[RFC4521]{RFC4521} Zeilenga, K., "Considerations for LDAP
   Extensions", BCP 118, RFC 4521, June 2006.
\bibitem[X.500]{X.500} [X.500]       International Telecommunication Union -
                 Telecommunication Standardization Sector, "The
                 Directory -- Overview of concepts, models and
                 services", X.500(1993) (also ISO/IEC 9594-1:1994).
\bibitem[X.501]{X.501} International Telecommunication Union -
                 Telecommunication Standardization Sector, "The
                 Directory -- Models", X.501(1993) (also ISO/IEC 9594-
                 2:1994).
\bibitem[X.511]{X.511} International Telecommunication Union -
                 Telecommunication Standardization Sector, "The
                 Directory: Abstract Service Definition", X.511(1993)
                 (also ISO/IEC 9594-3:1993).
